### 2021-09-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@97749228c7ffc006fb4863d4e501d0fcd761ae2c 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@fc74eeb831ab79a23c1728874edc8c81ff99994b 🚀

\vfill
Despite their importance in many ecological processes, collecting data
and information on ecological interactions, and therefore species
interaction networks, is an exceedingly challenging task. For this
reason, large parts of the world have a data deficit when it comes to
species interactions, and how the resulting networks are structured. As
data collection alone is unlikely to be sufficient at filling these
global gaps, community ecologists must adopt predictive methods. In this
contribution, we develop such a method, relying on graph embedding (the
extraction of explanatory latent variables from known graph structures)
and transfer learning (the application of previous solutions to novel
problems with limited predictors overlap) in order to assemble a
predicted list of trophic interactions between mammals of Canada. This
interaction list is derived from extensive knowledge of the mammalian
food web of Europe, despite the fact that there are fewer than 5\% of
common species between the two locations. The results of the predictive
model are compared against databases of recorded pairwise interactions,
showing that we correctly recover over 95\% of known interactions. We
provide guidance on how this method can be adapted by substituting some
approaches or predictors in order to make it more generally applicable.

@@

Finally, we downloaded the data from Strong \& Leroux (2014), who mined
various literature sources to identify trophic interactions in
Newfoundland. This dataset documented 25 interactions between mammals,
only two of which were not part of our (Canada-level) predictions,
resulting in a success rate of 92\%. These two interactions were added
to our predicted metaweb with a probability of 1.

>>>>

\vfill
Despite their importance in many ecological processes, collecting data
and information on ecological interactions is an exceedingly challenging
task. For this reason, large parts of the world have a data deficit when
it comes to species interactions, and how the resulting networks are
structured. As data collection alone is unlikely to be sufficient,
community ecologists must adopt predictive methods. Here we develop such
a method, relying on graph embedding and transfer learning to assemble a
predicted list of trophic interactions between Canadian mammals. This
interaction list is derived from the European food web, despite sharing
only 5\% of common species with Canada. The results of the predictive
model are compared against databases of recorded pairwise interactions,
showing that we correctly recover over 95\% of known interactions. We
provide guidance on how this method can be adapted by substituting some
approaches or predictors in order to make it more generally applicable.

@@

Finally, we downloaded the data from Strong \& Leroux (2014), who mined
various literature sources to identify trophic interactions in
Newfoundland. This dataset documented 25 interactions between mammals,
only two of which were not part of our (Canada-level) predictions,
resulting in a success rate of 92\%. These two interactions were added
to our predicted metaweb with a probability of 1. A table listing all
interactions in the predicted Canadian metaweb can be found in the
supplementary material.

### 2021-09-20 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@97749228c7ffc006fb4863d4e501d0fcd761ae2c 🚀
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@fc74eeb831ab79a23c1728874edc8c81ff99994b 🚀

Despite their importance in many ecological processes, collecting data
and information on ecological interactions, and therefore species
interaction networks, is an exceedingly challenging task. For this
reason, large parts of the world have a data deficit when it comes to
species interactions, and how the resulting networks are structured. As
data collection alone is unlikely to be sufficient at filling these
global gaps, community ecologists must adopt predictive methods. In this
contribution, we develop such a method, relying on graph embedding (the
extraction of explanatory latent variables from known graph structures)
and transfer learning (the application of previous solutions to novel
problems with limited predictors overlap) in order to assemble a
predicted list of trophic interactions between mammals of Canada. This
interaction list is derived from extensive knowledge of the mammalian
food web of Europe, despite the fact that there are fewer than 5\% of
common species between the two locations. The results of the predictive
model are compared against databases of recorded pairwise interactions,
showing that we correctly recover over 95\% of known interactions. We
provide guidance on how this method can be adapted by substituting some
approaches or predictors in order to make it more generally applicable.

>>>>

Despite their importance in many ecological processes, collecting data
and information on ecological interactions is an exceedingly challenging
task. For this reason, large parts of the world have a data deficit when
it comes to species interactions, and how the resulting networks are
structured. As data collection alone is unlikely to be sufficient,
community ecologists must adopt predictive methods. Here we develop such
a method, relying on graph embedding and transfer learning to assemble a
predicted list of trophic interactions between Canadian mammals. This
interaction list is derived from the European food web, despite sharing
only 5\% of common species with Canada. The results of the predictive
model are compared against databases of recorded pairwise interactions,
showing that we correctly recover over 95\% of known interactions. We
provide guidance on how this method can be adapted by substituting some
approaches or predictors in order to make it more generally applicable.
